---
title: "Refrigerator Sales Project"
author: "Elise Roche, Melody Shaff, Brian Clare, Carly Rose Willing, Joe Kass"
date: "October 10, 2017"
output: html_document
---

# Introduction 

In this project, we set out to determine which of the Energy Consumption Survey statistics are related to refrigerator ownership. We wanted to learn who the market audience is for different sizes and types of refrigerators, as well as glean who the primary purchasers are for multiple refrigerators. We examined the data in sets (household makeup, region of the country, climate, eco-friendly incentives, etc.) to find which variables were having an effect on refrigerator ownership in nuber, size, and type. We sought to draw meaningful conclusions about where (and where not) and who (and who not) to advertise refrigerators to, and further which refrigerators would be best received by these various groups. 

\pagebreak

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#load libraries
library(tidyverse)
library(grid)
library(gridExtra)

#input data
fridge <- read_csv("https://www.eia.gov/consumption/residential/data/2015/csv/recs2015_public_v1.csv") %>% 
select(KOWNRENT, NUMFRIG, SIZRFRI1, TYPERFR1, AGERFRI1, ICE, SIZRFRI2, AGERFRI2, LOCRFRI2, NUMFREEZ, NUMMEAL, REBATEAPP, RECYCAPP, TAXCREDITAPP, ESFREEZE, ESFRIG, EMPLOYHH, ATHOME, MONEYPY, DIVISION, UATYP10)
```



# Goals of Research

- Determine which of the Energy Consumption Survey statistics are related to refrigerator ownership

- Provide relevant areas to advertise refrigerators

- Point out groups that may be less valuable to advertise

```{r include = FALSE}
#clean the fridge data

fridge$AGERFRI1 <- apply(as.matrix(fridge[,5]), MARGIN = 2, function(x) {ifelse(x == -2, NA, x)})
fridge$AGERFRI1 <- apply(fridge[,5], MARGIN = 2, function(x) {ifelse(x == 5, 20, x)})
fridge$AGERFRI1 <- apply(fridge$AGERFRI1, MARGIN = 2, function(x) {ifelse(x == 42, 17, x)})
fridge$AGERFRI1 <- apply(fridge$AGERFRI1, MARGIN = 2, function(x) {ifelse(x == 41, 12, x)})
fridge$AGERFRI1 <- apply(fridge$AGERFRI1, MARGIN = 2, function(x) {ifelse(x == 3, 7, x)})
fridge$AGERFRI1 <- apply(fridge$AGERFRI1, MARGIN = 2, function(x) {ifelse(x == 2, 3, x)})

fridge$TYPERFR1 <- apply(fridge[,4], MARGIN = 2, function(x){ifelse(x == -2, NA, x)})
fridge$TYPERFR1 <- apply(fridge[,4], MARGIN = 2, function(x){ifelse(x == 21 | x == 22 | x == 23, 2, x)})
fridge$TYPERFR1 <- apply(fridge[,4], MARGIN = 2, function(x){ifelse(x == 5, 3, x)})

fridge$ICE <- apply(fridge[,6], MARGIN = 2, function(x){ifelse(x == -2, NA, x)})
fridge$ICE <- apply(fridge[,6], MARGIN = 2, function(x){ifelse(x == 1, "Ice", x)})
fridge$ICE <- apply(fridge[,6], MARGIN = 2, function(x){ifelse(x == 0, "No Ice", x)})

fridge$KOWNRENT <- apply(fridge[,1], MARGIN = 2, function(x){ifelse(x == 1, "Owned", x)})
fridge$KOWNRENT <- apply(fridge[,1], MARGIN = 2, function(x){ifelse(x == 2, "Rented", x)})
fridge$KOWNRENT <- apply(fridge[,1], MARGIN = 2, function(x){ifelse(x == 3, "Other", x)})

fridge$SIZRFRI1 <- apply(fridge[,3], MARGIN = 2, function(x){ifelse(x == -2, NA, x)})

fridge$LOCRFRI2 <- apply(fridge[,9], MARGIN = 2, function(x){ifelse(x == -2, NA, x)})
fridge$LOCRFRI2 <- apply(fridge[,9], MARGIN = 2, function(x){ifelse(x == 1, "Basement", x)})
fridge$LOCRFRI2 <- apply(fridge[,9], MARGIN = 2, function(x){ifelse(x == 2, "Garage", x)})
fridge$LOCRFRI2 <- apply(fridge[,9], MARGIN = 2, function(x){ifelse(x == 3, "Outside", x)})
fridge$LOCRFRI2 <- apply(fridge[,9], MARGIN = 2, function(x){ifelse(x == 4, "Main Floor", x)})
fridge$LOCRFRI2 <- apply(fridge[,9], MARGIN = 2, function(x){ifelse(x == 9, "Other", x)})



rebate1 <- filter(fridge, REBATEAPP > -1)
rebate2 <- filter(fridge, RECYCAPP > -1)
rebate3 <- filter(fridge, TAXCREDITAPP > -1)
```

# General Refrigerator Size

- Overall, categories 3 and 4 are the most popular sizes of primary refrigerator
- 1 and 5 barely exist
- Larger refrigerators are more likely to have ice dispensers

```{r warning = FALSE}
ggplot(data = fridge, mapping = aes(x = SIZRFRI1)) + 
  geom_bar(mapping = aes(fill = ICE)) +
  labs(x = "Size of Primary Refrigerator", y="Households", fill = "Ice dispenser")
```
  
\pagebreak  
  
# Second Refrigerator size

- Second refrigerators are much more likely to be small, but there are still more midsize 2nd refrigerators
- Most common locations of 2nd refrigerators are basement, garage and main floor
- Smaller second refrigerators more likely on main floor
- Second refrigerator in garage or basement is more likely midsize

``` {r warning = FALSE}
ggplot(data = filter(fridge, SIZRFRI2 > 0), mapping = aes(x = SIZRFRI2)) +
  geom_bar(mapping = aes(fill = LOCRFRI2)) +
  labs(x = "Size of 2nd Refrigerator", y = "Households", fill = "Location of 2nd Refrigerator")
```

# Most refrigerators have 2 doors in some configuration. Ice dispensers are less than 50% of 2-door models

```{r warning = FALSE}
ggplot(data = fridge, mapping = aes(x = TYPERFR1)) + 
  geom_bar(mapping = aes(fill = ICE)) +
  labs(x = "Doors of Primary Refrigerator", y = "Households", fill = "Ice dispenser")
```

\pagebreak

# Rebates and Tax Incentives

Data regarding the effectiveness of monetary incentives shows that those who recieve them are more likely to purchase a refridgorator. The dataset shows that people are more likely to own multiple refrigerators if they received a rebate or tax credit. Likewise, people were received these incentives more likely to have a newer refrigerator. This suggests that incentives like rebates and tax credits influence whether or not consumers purchase new or additional refrigerators. The data also shows that incentives influence whether consumers will invest more in these refrigerators. 3-door refrigerators are more expensive than their simpler counterparts, and are purchased more by rebate holders. Thus, offering a monetary incentive for customers for higher-end products would be worthwhile.

# Number of Refrigerators Owned vs. Rebates

Those who receive rebates are more likely to own multiple refrigerators.


```{r}
# subsets those who did and did not receive a rebate from supplier for buying a new appliance; 
#makes bar graphs showing number of refrigerators for each group
yrebate<-filter(rebate1, REBATEAPP==1)
plot1 <- ggplot(data=yrebate) + geom_bar(data=yrebate, aes(x=NUMFRIG, fill=as.factor(NUMFRIG)), show.legend=FALSE) + labs(x="Number of Refrigerators in Household", y="Households", title="Respondent Received Rebate from Utility Supplier") 
nrebate <-filter(rebate1, REBATEAPP==0)
plot2<- ggplot(data=nrebate) + geom_bar(data=nrebate, aes(x=NUMFRIG, fill=as.factor(NUMFRIG)), show.legend=FALSE) + labs(x="Number of Refrigerators in Household",y="Households", title="Respondent Did Not Receive Rebate from Utility Supplier")

# subsets those who did and did not receive a rebate for recycling an old appliance; 
#makes bar graphs showing number of refrigerators for each group
yrrebate<-filter(rebate2, RECYCAPP==1)
plot3<- ggplot(data=yrrebate) + geom_bar(data=yrrebate, aes(x=NUMFRIG, fill=as.factor(NUMFRIG)), show.legend=FALSE) + labs(x="Number of Refrigerators in Household",y="Households", title="Respondent Received Rebate for Recycling Old Appliance") 
nrrebate <-filter(rebate2, RECYCAPP==0)
plot4<-ggplot(data=nrrebate) + geom_bar(data=nrrebate, aes(x=NUMFRIG, fill=as.factor(NUMFRIG)), show.legend=FALSE) + labs(x="Number of Refrigerators in Household",y="Households", title="Respondent Did Not Receive Rebate for Recycling Appliance")

# subsets those who did and did not receive a tax credit for buying a new appliance; 
#makes bar graphs showing number of refrigerators for each group
ytrebate<-filter(rebate3, TAXCREDITAPP==1)
plot5<-ggplot(data=ytrebate) + geom_bar(data=ytrebate, aes(x=NUMFRIG, fill=as.factor(NUMFRIG)), show.legend=FALSE) + labs(x="Number of Refrigerators in Household",y="Households", title="Respondent Received Tax Credit") 
ntrebate <-filter(rebate3, TAXCREDITAPP==0)
plot6<-ggplot(data=ntrebate) + geom_bar(data=ntrebate, aes(x=NUMFRIG, fill=as.factor(NUMFRIG)), show.legend=FALSE) + labs(x="Number of Refrigerators in Household", y="Households",title="Respondent Did Not Receive Tax Credit")

plot1 <- plot1 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot2 <- plot2 + theme(plot.title = element_text( size = 8), axis.title=element_text(size = 7))
plot3 <- plot3 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot4 <- plot4 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot5 <- plot5 + theme(plot.title = element_text( size = 9), axis.title=element_text(size = 7))
plot6 <- plot6 + theme(plot.title = element_text( size = 9), axis.title=element_text(size = 7))
grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2)
```

\pagebreak

# Age of Primary Refrigerator vs. Rebates

Newer refrigerators are more common with rebates

```{r warning = FALSE}

# subsets those who did and did not receive a rebate from supplier for buying a new appliance; 
#makes bar graphs showing age of main refrigerator for each group
yrebate<-filter(rebate1, REBATEAPP==1)
plot1 <- ggplot(data=yrebate) + geom_bar(data=yrebate, aes(x=AGERFRI1, fill=as.factor(AGERFRI1)), show.legend=FALSE) + labs(x="Age of Refrigerator", y= "Households", title="Respondent Received Rebate from Utility Supplier") 
nrebate <-filter(rebate1, REBATEAPP==0)
plot2 <- ggplot(data=nrebate) + geom_bar(data=nrebate, aes(x=AGERFRI1, fill=as.factor(AGERFRI1)), show.legend=FALSE) + labs(x="Age of Refrigerator", y= "Households",  title="Respondent Did Not Receive Rebate from Utility Supplier") 

# subsets those who did and did not receive a rebate for recycling an old appliance; 
#makes bar graphs showing age of main refrigerator for each group
yrrebate<-filter(rebate2, RECYCAPP==1)
plot3 <- ggplot(data=yrrebate) + geom_bar(data=yrrebate, aes(x=AGERFRI1, fill=as.factor(AGERFRI1)), show.legend=FALSE) + labs(x="Age of Refrigerator",  y= "Households", title="Respondent Received Rebate for Recycling Old Appliance") 
nrrebate <-filter(rebate2, RECYCAPP==0)
plot4 <- ggplot(data=nrrebate) + geom_bar(data=nrrebate, aes(x=AGERFRI1, fill=as.factor(AGERFRI1)), show.legend=FALSE) + labs(x="Age of Refrigerator",  y= "Households", title="Respondent Did Not Receive Rebate for Recycling Old Appliance")

# subsets those who did and did not receive a tax credit for buying a new appliance; 
#makes bar graphs showing age of main refrigerator for each group
ytrebate<-filter(rebate3, TAXCREDITAPP==1)
plot5 <- ggplot(data=ytrebate) + geom_bar(data=ytrebate, aes(x=AGERFRI1, fill=as.factor(AGERFRI1)), show.legend=FALSE) + labs(x="Age of Refrigerator",  y= "Households", title="Respondent Received Tax Credit for Purchasing Appliance") 
ntrebate <-filter(rebate3, TAXCREDITAPP==0)
plot6 <- ggplot(data=ntrebate) + geom_bar(data=ntrebate, aes(x=AGERFRI1, fill=as.factor(AGERFRI1)), show.legend=FALSE) + labs(x="Age of Refrigerator",  y= "Households", title="Respondent Did Not Receive Tax Credit for Purchasing Appliance")


plot1 <- plot1 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot2 <- plot2 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot3 <- plot3 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot4 <- plot4 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot5 <- plot5 + theme(plot.title = element_text( size = 6), axis.title=element_text(size = 7))
plot6 <- plot6 + theme(plot.title = element_text( size = 6), axis.title=element_text(size = 7))
grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2)
```

* Age of Refrigerator represents average number of range in data

\pagebreak 

# Type of Refrigerator vs. Rebate
Larger refrigerators are more common with rebates

```{r warning = FALSE}
# subsets those who did and did not receive a rebate from supplier for buying a new appliance; 
#makes bar graphs showing type of main refrigerator for each group
yrebate<-filter(rebate1, REBATEAPP==1)
plot1 <- ggplot(data=yrebate) + geom_bar(data=yrebate, aes(x=TYPERFR1, fill=as.factor(TYPERFR1)), show.legend=FALSE) + labs(x="Number of Doors", y= "Households", title="Respondant Received Rebate from Utility Supplier")
nrebate <-filter(rebate1, REBATEAPP==0)
plot2 <- ggplot(data=nrebate) + geom_bar(data=nrebate, aes(x=TYPERFR1, fill=as.factor(TYPERFR1)), show.legend=FALSE) + labs(x="Number of Doors", y= "Households", title="Respondant Did Not Receive Rebate from Utility Supplier")

# subsets those who did and did not receive a rebate for recycling an old appliance; 
#makes bar graphs showing type of main refrigerator for each group
yrrebate<-filter(rebate2, RECYCAPP==1)
plot3 <- ggplot(data=yrrebate) + geom_bar(data=yrrebate, aes(x=TYPERFR1, fill=as.factor(TYPERFR1)), show.legend=FALSE) + labs(x="Number of Doors", y= "Households", title="Respondant Received Rebate for Recycling Old Appliance")
nrrebate <-filter(rebate2, RECYCAPP==0)
plot4 <- ggplot(data=nrrebate) + geom_bar(data=nrrebate, aes(x=TYPERFR1, fill=as.factor(TYPERFR1)), show.legend=FALSE) + labs(x="Number of Doors", y= "Households", title="Respondant Did Not Receive Rebate for Recycling Old Appliance")

# subsets those who did and did not receive a tax credit for buying a new appliance; 
#makes bar graphs showing type of main refrigerator for each group
ytrebate<-filter(rebate3, TAXCREDITAPP==1)
plot5 <- ggplot(data=ytrebate) + geom_bar(data=ytrebate, aes(x=TYPERFR1, fill=as.factor(TYPERFR1)), show.legend=FALSE) + labs(x="Number of Doors", y= "Households", title="Respondant Received Tax Credit for Purchasing Appliance") 
ntrebate <-filter(rebate3, TAXCREDITAPP==0)
plot6 <- ggplot(data=ntrebate) + geom_bar(data=ntrebate, aes(x=TYPERFR1, fill=as.factor(TYPERFR1)), show.legend=FALSE) + labs(x="Number of Doors", y= "Households", title="Respondant Did Not Receive Tax Credit for Purchasing Appliance")


plot1 <- plot1 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot2 <- plot2 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot3 <- plot3 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot4 <- plot4 + theme(plot.title = element_text( size = 7), axis.title=element_text(size = 7))
plot5 <- plot5 + theme(plot.title = element_text( size = 6), axis.title=element_text(size = 7))
plot6 <- plot6 + theme(plot.title = element_text( size = 6), axis.title=element_text(size = 7))
grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2)
```

\pagebreak

# Homeowner Status vs. Refrigerator sales

The data shows that most refrigerators are owned by people who also own their place of residence. Homeowners are also more likely to own more than one refrigerator than those who rent. It is uncommon for renters to have refrigerators with three-door designs, which means that renters would be less likely to purchase a more expensive model.

# Homeowners are the primary market:
```{r}
ggplot(data = fridge, mapping = aes(x = NUMFRIG, fill = KOWNRENT)) + 
  geom_histogram(binwidth = 1)  +
  facet_wrap(~ as.factor(KOWNRENT), nrow=3) +
  scale_fill_hue(name="Home Ownership Status", labels=c("Other", "Own", "Rent")) +
  labs(title="Number of Refrigerators vs. Home Ownership Status", x="Number of Refrigerators", y = "Households")
```

# Renters have less expensive refrigerators:
```{r warning = FALSE}
ggplot(data=fridge, mapping=aes(x=TYPERFR1, fill = KOWNRENT)) +
  geom_histogram(binwidth = 1) + facet_wrap(~ as.factor(KOWNRENT), nrow=3) +
  scale_fill_hue(name="Home Ownership Status", labels=c("Other", "Own", "Rent")) +
  labs(title="Type of Refrigerator vs. Home Ownership Status", x="Number of Refrigerator Doors", y = "Households")
```

# Homeowners buy larger refrigerators:
```{r warning = FALSE}
ggplot(data=fridge, mapping=aes(x=SIZRFRI1, fill = KOWNRENT)) + 
  geom_histogram(binwidth = 1) + facet_wrap(~ as.factor(KOWNRENT), nrow=3) + 
  scale_fill_hue(name="Home Ownership Status", labels=c("Other", "Own", "Rent")) +
  labs(title="Size of Primary Refrigerator and Home Ownership", x="Size of Refrigerator (smallest to largest)",  y = "Households")
```

# Homeowners more likely to have luxury refrigerators with ice dispensors
```{r warning = FALSE}
ggplot(data=fridge, mapping=aes(x=ICE, fill = KOWNRENT)) +
  geom_bar() + facet_wrap(~ as.factor(KOWNRENT), nrow=3) +
  scale_fill_hue(name="Home Ownership Status", labels=c("Other", "Own", "Rent")) +
  labs(title="In-Door Ice and Home Ownership", x="In-Door Ice Machine (0=No Ice and 1=Ice)",  y = "Households")
```

\pagebreak

# Location in the United States as it correlates to refrigerator ownership

Some areas of the United States have increased rates of refrigerator ownership. This may be due to a variety of factors like available supermarkets, climate, and food customs. Advertising to the places that have more people who own multiple refrigerators will likely be more succesful than in other areas where this is less common.


```{r warning=FALSE, message=FALSE}
ggplot(data=fridge, mapping=aes(x = DIVISION, y = NUMFRIG, color = as.factor(DIVISION))) + 
  geom_jitter() + geom_smooth(se = FALSE) + labs(title="Number of Refrigerators vs. Geographic Census Division", y="Number of Refrigerators", x="Geographic Division") +
  scale_colour_hue(name="Geographic Division", labels=c("New England", "MidAtlantic", "ENC", "WNC", "SouthAtlantic", "ESC","WSC","MNo","MSo","Pacific"))
```

#T-Test for Difference of Means 

Because the sample size for each census division is different, the plot does not give us as much information as we would like. After running an indepedent t-test for difference in means, comparing each region to the national average, the following information was found: 

Division     | Average #      | p-value | Signficant?
-------------| -------------- |---------|------------
Nationally   | 1.395          |         |
New England  | 1.352          | 0.2692  |
MidAtlantic  | 1.447          | 0.0933  | *
ENC          | 1.419          | 0.3379  |
WNC          | 1.501          | 0.0019  | **
S.Atlantic   | 1.368          | 0.2145  |
ESC          | 1.323          | 0.031   | **
WSC          | 1.384          | 0.7393  |
Mountain N.  | 1.496          | 0.0409  | **
Mountain S.  | 1.335          | 0.125   |
Pacific      | 1.363          | 0.124


Based on this information, we can conclude, at reasonable \alpha levels, that people in the MidAtlantic, WNC, and Mountain N. have more refrigerators on average than the average national number. Those in ESC have fewer refrigerators on average. As stated before, this may be due in part to lack of availability of grocery stores in the region, or different culinary customs.

```{r warning = FALSE}
#this chunks the indices for each division so that other data may be stratified based on division
NewEngland <- which(fridge$DIVISION %in% c(1))
MidAt <- which(fridge$DIVISION %in% c(2)) 
ENC <- which(fridge$DIVISION %in% c(3))
WNC <- which(fridge$DIVISION %in% c(4))
SoAt <- which(fridge$DIVISION %in% c(5))
ESC <- which(fridge$DIVISION %in% c(6))
WSC <- which(fridge$DIVISION %in% c(7))
MNo <- which(fridge$DIVISION %in% c(8))
MSo <- which(fridge$DIVISION %in% c(9))
Pacific <- which(fridge$DIVISION %in% c(10))

#This finds the number of fridges per household based on which geographic division they reside in
NewEngland1 <- fridge$NUMFRIG[NewEngland]
MidAt1 <- fridge$NUMFRIG[MidAt]
ENC1 <- fridge$NUMFRIG[ENC]
WNC1 <- fridge$NUMFRIG[WNC]
SoAt1 <- fridge$NUMFRIG[SoAt]
ESC1 <- fridge$NUMFRIG[ESC]
WSC1 <- fridge$NUMFRIG[WSC]
MNo1 <- fridge$NUMFRIG[MNo]
MSo1 <- fridge$NUMFRIG[MSo]
Pacific1 <- fridge$NUMFRIG[Pacific]

#this is an independent t-test to test if the average number of fridges per geographic division is the same or different from the national average
t.test(fridge$NUMFRIG, NewEngland1) 
t.test(fridge$NUMFRIG, MidAt1)
t.test(fridge$NUMFRIG, ENC1)
t.test(fridge$NUMFRIG, WNC1) 
t.test(fridge$NUMFRIG, SoAt1)
t.test(fridge$NUMFRIG, ESC1)
t.test(fridge$NUMFRIG, WSC1)
t.test(fridge$NUMFRIG, MNo1)
t.test(fridge$NUMFRIG, MSo1)
t.test(fridge$NUMFRIG, Pacific1)
```

\pagebreak

# Areas with multiple refrigerator households:
Of those who have two or more refrigerators, it seems as though the Mid Atlantic, West North Central, and East North Central are where the majority of the households reside. Similarly, as shown, of those households without a refrigerator, the majority of the households reside in the West South Central or South Atlantic regions. This is interesting particularly for the West South Central region because the sample size is lower, indicating that the lack of refrigerators may be due to a geographic variable. 
1 = New England  
2 = Mid Atlantic  
3 = East North Central  
4 = West North Central  
5 = South Atlantic  
6 = East South Central  
7 = West South Central  
8 = Mountain North  
9 = Mountain South  
10 = Pacific  

```{r message=FALSE}
#This chunk looks only at those who have 2+ refrigerators 
y <- which(fridge$NUMFRIG %in% c(2, 3, 4, 5, 6, 7, 8))
mark1 <-fridge$DIVISION[y]

#this plots those who have 2+ refrigerators based on their geographic division
mark1 <- data.frame(x=mark1)
ggplot(mark1, aes(x=x))+
  geom_histogram(binwidth=1,color="black", fill="grey")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10))+
  labs(title="Geographic Division of those with 2 or More Refrigerators", x="Geographic Division", y="Number of Households with 2+ Refrigerators")
```
```{r message = FALSE}
#this chunk looks at homes with 0 refrigerators
zero <- which(fridge$NUMFRIG %in% c(0))
mark <- fridge$DIVISION[zero]
mark <- data.frame(x=mark)
ggplot(mark, aes(x=x))+
  geom_histogram(binwidth=1,color="black", fill="grey")+
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10))+
  labs(title="Geographic Division of those with 0 Refrigerators", x="Geographic Division", y="Number of Households with 0 Refrigerators")
```

#Age of Refrigerator Based on Geographic Location
Based on the figure below, we can see that those in the Mountain North region have fewer refrigerators over 5-7 years old. In comparison, those in the MidAtlantic region have a higher concentration of older refrigerators when looking at the corresponding sample sizes. As a result, one can look to the regions containing a larger number of older refrigerators when marketing replacements.
```{r message = FALSE, warning=FALSE}
ggplot(data=fridge, mapping=aes(x=DIVISION, y=AGERFRI1, color=as.factor(DIVISION))) + 
  geom_jitter() + geom_smooth(se=FALSE) + labs(title="Age of Most Used Refrigerator vs. Geographic Region", x="Geographic Region", y="Age of Most Used Refrigerator") +
  scale_colour_hue(name="Geographic Region", labels=c("New England", "MidAtlantic", "ENC", "WNC", "SouthAtlantic", "ESC","WSC","MNo","MSo","Pacific"))

```

#Urban Type also impacts number of Freezers
From just looking at the figure below, it is evident that those in Rural areas have more separate freezers than those who live in Urban areas or Urban Clusters. This is likely due to increased distance between home and the grocery store, making larger grocery trips more efficient. With this information, we can choose to market refrigerators with larger freezers to individuals in rural areas so that they do not have to rely as much on their extra freezer.

```{r message = FALSE}
#This plots the number of refrigerators vs the urban location type 
ggplot(data = fridge, mapping = aes(x = UATYP10, y = NUMFREEZ, color = as.factor(UATYP10))) + geom_jitter() + geom_smooth(se = FALSE) + labs(title="Number of Freezers vs. Urban Type", x="Urban Type", y="Number of Freezers")+ scale_colour_hue(name="Location Type", labels=c("Urban Cluster","Rural","Urban Area"))
```

# Retired and Fully employed people are most likely to own multiple refrigerators:
As a result, a marketing campaign aimed more towards those who are Retired or Fully Employed. They may have higher rates of refrigerator ownership due to having incomes which place them in an economically stable position where they feel more comfortable buying more "luxury" type goods.
```{r message=FALSE}
#this plots the number of fridges for each employment status
ggplot(data=fridge, mapping=aes(x=EMPLOYHH, y=NUMFRIG, color=as.factor(EMPLOYHH))) + 
  geom_jitter() + geom_smooth(se=FALSE) + labs(title="Number of Refrigerator vs. Employment Status of Household", x="Employment Status", y="Number of Refrigerator") +
  scale_colour_hue(name="Employment Status", labels=c("Retired","Full Time","Part Time"))

```

\pagebreak

# The Culinarily Inclined own more refrigerators

People that cook more hot meals own more refrigerators, which makes them an obvious group to advertise to. They also are more likely to own refrigerators that are extrema on the size spectrum; meaning that those who cook often are more likely to own very large or small refrigerators in addition to those who own the most common sizes.

```{r}
#Amount of Hot meals cooked against fridges
ggplot(data=fridge, aes(x=NUMMEAL, y=NUMFRIG,color=as.factor(NUMMEAL))) + geom_jitter() +
labs(title= "Meals cooked vs. Number of Refrigerators owned",x="Number of Meals Cooked",y="Number of Refrigerators") +
scale_colour_hue(name="")

```


# The largest and smallest refrigerators are bought by those who cook more frequently:
```{r warning = FALSE}
ggplot(data=fridge, aes(x=NUMMEAL, y=SIZRFRI1, color=as.factor((NUMMEAL)))) + geom_jitter() +
labs(title="Meals cooked vs. Size of Refrigerator",x="Number of Meals Cooked",y="Size of Refrigerator") +
  scale_colour_hue(name="")

```

\pagebreak

# Final Conclusions

Over the course of our exploration, we found that folks living in the Mid-Atlantic tend to have older refrigerators and, thus, may be in the market for upgrades. We also found that rural communities are more likely to have larger refrigerators than urban clusters, which could also be linked to homeownership as owners are more likely to own large refrigerators than renters. Thus, rural homeowners provide the optimum market for large refrigerators. Money also plays a role in refrigerator ownership, as those who received rebates are more likely to own more and more expensive refrigerators. In light of this, marketing higher-end refrigerators to those with these monetary incentives is a worthwhile endeavor as they are more likely to purchase these products. We also found, relatively unsurprisingly, that those who cook more meals per week are more likely to own more refrigerators. All of these factors, we can predict, give us a few key groups to target: rural homeowners for large refrigerators; urban renters for smaller, more basic refrigerator designs; homeowners in areas with monetary incentives for eco-friendly refrigerator upgrades with high-end refrigerators; and Mid-Atlantic dwellers for updates on their largely out-dated refrigerators.      

